Hypertension and microbiome

### 2019-10-07 articletwo.Rmd
Adjusted

    dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq, ~HYPERTENSION)

@@

```{r deseq plot}
g.deseq <- results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    ggplot(aes(x=Feature, y=log2FoldChange, color=qval)) +
    geom_point(size=1) +
    geom_hline(yintercept = 0, color = "gray") +
    theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)) +
    coord_flip() +
    theme_classic()

ggsave(file = "cache/deseq.png", plot=g.deseq, height=10, width=5)
```

>>>>

@@

```{r deseq plot}
g.deseq <- results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    dplyr::mutate(group = dplyr::ntile(row_number(), 3)) %>%
    ggplot(aes(x=Feature, y=log2FoldChange, color=qval, group = group)) +
    facet_wrap(~group, scales = "free_y") +
    geom_point(size=1) +
    geom_hline(yintercept = 0, color = "gray") +
    theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)) +
    coord_flip() +
    theme_classic()

ggsave(file = "cache/deseq.png", plot=g.deseq, height=10, width=15)
```
